---
title: "SDP Knockoffs"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{SDP Knockoffs}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

Overview
--------

The knockoff package supports two styles of knockoff variables, *equicorrelated* knockoffs (the default) and *semidefinite programming* (SDP) knockoffs. Though more computationally expensive, the SDP knockoffs are statistically superior by having higher power. Unfortunately, the R programming environment has poor support for semidefinite programming. To create SDP knockoffs, this package relies on the Python library [CVXPY][cvxpy].

The knockoff package will automatically invoke the Python interpreter to create SDP knockoffs provided that (1) you have a Python installation with CVXPY and (2) R can find your Python interpreter. Thus, to use SDP knockoffs you should:

1) **Install Python and CVXPY**

On Unix platforms this is usually straightforward. If you don't have a Python installation, follow the [instructions included with CVXPY][cvxpy-install]. If you already have Python (along with NumPy and SciPy), running `pip install cvxpy` will likely work.
   
On Windows, matters are more complicated. You can attempt the [instructions for Windows included with CVXPY][cvxpy-install-windows]. Alternatively, you can skip the compilation process by using pre-compiled binaries, according to the alternative installation instructions provided below.
   
2) **Verify that R can find the Python interpretator**

Launch on your R environment. On Unix, run
```{r, eval=F}
system('which python')
```
or on Windows, run
```{r, eval=F}
system('where python')
```
You should see the path to your Python installation. If not, adjust your `PATH` environment variable appropriately.

[cvxpy]: http://cvxpy.org
[cvxpy-install]: http://www.cvxpy.org/en/latest/install/index.html
[cvxpy-install-windows]: http://www.cvxpy.org/en/latest/install/index.html#windows

Installation instructions for Windows
-----------------

These alternative instructions for MS Windows use pre-compiled binaries.

1) Download and install [Python 2.7][python27]

**Note**: Even if you are running 64-bit Windows, make sure to use the 32-bit Python binaries. Due to a [bug][bug-win64] in `cvxopt`, CVXPY is effectively broken on 64-bit Windows.

2) Prepend the string
```
C:\Python27\;C:\Python27\Scripts\
```
to your `PATH` environment variable

3) Download and install the following binaries created by [Christoph Gohlke][gohlke]:
  - NumPy-MKL
  - SciPy
  - ECOS
  - cvxopt
  
4) Open the Windows command prompt (not the Python interpreter) and run the following commands:
```
pip install toolz
pip install cvxpy --no-deps
```

You should now have a working CVXPY installation.

**Note**: At the time of this writing, there are no pre-compiled binaries for SCS, an optional dependency of CVXPY. If SCS is not installed, CVXPY will emit warnings but will nonetheless function correctly. However, CVXPY 0.2.15 and older contain a bug that causes the warning logic to fail. If you encounter this problem, open the file
```
C:\Python27\Lib\site-packages\cvxpy\problems\solvers\scs_intf.py
```
and add the line `import warnings` as indicated [here][bug-cvxpy-warnings].

[python27]: https://www.python.org/downloads/release/python-279/
[gohlke]: http://www.lfd.uci.edu/~gohlke/pythonlibs/
[bug-win64]: https://github.com/cvxgrp/cvxpy/issues/102
[bug-cvxpy-warnings]: https://github.com/cvxgrp/cvxpy/blame/87a001910e64444efd16b33c206f4a1fbab3b8b2/cvxpy/problems/solvers/scs_intf.py#L22