---
title: "Using the Knockoff Filter"
author: "Evan Patterson"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using the Knockoff Filter}
  %\VignetteEngine{knitr::rmarkdown}
  %\usepackage[utf8]{inputenc}
---
```{r, echo=F}
set.seed(4567)
```

This vignette illustrates the basic and advanced usage of `knockoff.filter`. For simplicity, we will use synthetic data constructed such that the true coefficient vector $\beta$ has very few nonzero entries.

```{r}
# Problem parameters
n = 600          # number of observations
p = 200          # number of variables
k = 30           # number of variables with nonzero coefficients
amplitude = 3.5  # signal amplitude (for noise level = 1)

# Problem data
X = matrix(rnorm(n*p), nrow=n, ncol=p)
nonzero = sample(p, k)
beta = amplitude * (1:p %in% nonzero)
y.sample <- function() X %*% beta + rnorm(n)
```

First examples
--------------

To begin, we call `knockoff.filter` with all the default settings.
```{r}
library(knockoff)

y = y.sample()
result = knockoff.filter(X, y)
print(result)
```

The false discovery proportion is
```{r}
fdp <- function(selected) sum(beta[selected] == 0) / max(1, length(selected))
fdp(result$selected)
```
This is below the default FDR target of 0.20.

By default, the knockoff filter uses a test statistic based on the lasso. Specifically, it uses the statistic `knockoff.stat.lasso_signed_max`, which computes
$$
W_j = \max(Z_j, \tilde{Z}_j) \cdot \mathrm{sgn}(Z_j - \tilde{Z}_j),
$$
where $Z_j$ and $\tilde{Z}_j$ are the maximum values of the regularization parameter $\lambda$ at which the $j$th variable and its knockoff, respectively, enter the lasso model.

The knockoff package includes several other test statistics, all of which have names prefixed with `knockoff.stat`. In the next snippet, we use a statistic based on forward selection. We also set a lower target FDR of 0.10.
```{r}
result = knockoff.filter(X, y, fdr = 0.10, statistic = knockoff.stat.fs)
fdp(result$selected)
```

User-defined test statistics
----------------------------

In addition to using the predefined test statistics, it is also possible to define your own test statistics. To illustrate this possibility, we implement one of the simplest test statistics from the knockoff filter paper, namely
$$
W_j = \left|X_j^\top \cdot y\right| - \left|\tilde{X}_j^\top \cdot y\right|.
$$

```{r}
my_knockoff_stat <- function(X, X_ko, y) {
  abs(t(X) %*% y) - abs(t(X_ko) %*% y)
}
result = knockoff.filter(X, y, statistic = my_knockoff_stat)
fdp(result$selected)
```

Advanced usage
--------------

The function `knockoff.filter` is a wrapper around several simpler functions that

1. Construct knockoff variables (`knockoff.create`)
2. Compute the test statistic $W$ (various functions with prefix `knockoff.stat`)
3. Compute the threshold for variable selection (`knockoff.threshold`)

These functions may be called directly if desired. For more information, see the documentation for the individual functions.

**Warning**. The high-level function `knockoff.filter` will automatically normalize the columns of the input matrix (unless this behavior is explicitly disabled). However, all other functions in this package assume that the columns of the input matrix have unit Euclidean norm. Please be aware of these conventions.